Follow-up Samples

### 2017-01-13 submission/manuscript_outline_20161024.Rmd
complete result addition of common OTUs

***Common OTUs to both Lesion and Initial and Follow Up Models***
There were a total of `r length(common_vars_summary$otu)` OTUs that were common to both models.  Of these OTUs the most common taxonomic identifications were to  `r common_vars_summary['Otu000012', 'lowest_ID']`, `r common_vars_summary['Otu000005', 'lowest_ID']`, `r common_vars_summary['Otu000082', 'lowest_ID']`, and `r paste(gsub("_unclassified", "", common_vars_summary['Otu000006', 'lowest_ID']))`.

@@

**Figure 2: Previously Associated CRC Bacteria in Initial and Follow up Samples.**  A) Carcinoma initial and follow up samples. There was a significant difference in initial and follow up sample for the OTUs classfied as Peptostreptococcus stomatis (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas asaccharolytica (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`).  B) Adenoma initial and follow up samples.  There were no significant differences between initial and follow up.

>>>>

***Common OTUs to both Lesion and Initial and Follow Up Models***
There were a total of `r length(common_vars_summary$otu)` OTUs that were common to both models.  Of these OTUs the most common taxonomic identifications were to  `r common_vars_summary['Otu000012', 'lowest_ID']`, `r common_vars_summary['Otu000005', 'lowest_ID']`, `r common_vars_summary['Otu000082', 'lowest_ID']`, and `r paste(gsub("_unclassified", "", common_vars_summary['Otu000006', 'lowest_ID']))`.  The majority of these OTUs had taxonomic identification to bacteria typically thought of as commensal [Table S2].

@@

**Figure 2: Previously Associated CRC Bacteria in Initial and Follow up Samples.**  A) Carcinoma initial and follow up samples. There was a significant difference in initial and follow up sample for the OTUs classfied as Peptostreptococcus stomatis (P-value = `r format(main_crc_bugs_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas asaccharolytica (P-value = `r format(main_crc_bugs_summary["porp", "crc_BH"], digits = 3)`).  B) Adenoma initial and follow up samples.  There were no significant differences between initial and follow up.
